\begin{招待講演}{1}

\bibitem{kobayashi3-1}
Hill Hiroki Kobayashi, mdx: A Cloud Platform for Supporting Data Science and Cross-Disciplinary Research Collaborations, the Nepal JSPS Alumni Association (NJAA), hosted its 7th Symposium, 29 November, 2022.

\bibitem{kobayashi3-2}
小林博樹, mdx を用いたフィールドデータの蓄積と公開の可能性, 東京大学大学院農学生命科学研究科附属演習林 生態水文学研究所100周年記念式典, 8 Dec, 2022.

\bibitem{ykuga37056192}
空閑洋平, クラウド環境におけるネットワークインタフェースの高機能化, 第155回 システムソフトウェアとオペレーティング・システム研究会, 26 May, 2022.


\bibitem{fugaku} 鈴村豊太郎「夢の形～未来のコンピュータ～」（パネリスト）、スーパーコンピュータ「富岳」第2回成果創出加速プログラムシンポジウム「富岳百景」、2022年12月21日
\bibitem{jsse1}鈴村豊太郎,「データ活用社会創成プラットフォームmdxおよび 大規模グラフニューラルネットワーク」, 第34回CCSEワークショップ「原子力材料研究開発におけるDX推進の現状と将来：原子力材料研究開発の革新と新展開」, 2023年2月24日
\bibitem{jsse2}鈴村豊太郎,「人工知能の最先端研究に迫る ～大規模グラフニューラルネットワークの世界へ」, 東京大学柏キャンパス一般公開2022、特別講演会、2022年10月22日
\bibitem{rakuten}Toyotaro Suzumura, “How Will Data and AI Change the World?”,  Rakuten Optimism Conference, Tokyo, Japan, September 29, 2022
\bibitem{rccs}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, The 5th R-CCS International Symposium, Kobe Japan, February 7, 2023
\bibitem{france}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, International Workshop “HPC challenges for new extreme scale application” held by French Alternative Energies and Atomic Energy Commission, Paris, France, March 6, 2023
\bibitem{barcelona}Toyotaro Suzumura,  “Large-Scale Graph Neural Networks for Real-World Industrial Applications”, Barcelona Supercomputing Center, Barcelona, Spain, March 10, 2023
\end{招待講演}

\begin{招待論文}{1}


\bibitem{02早川智彦01}
早川智彦, 東晋一郎: 時速100km走行での覆工コンクリート高解像度変状検出手法, 建設機械, vol.58, no.4, pp.34-38, 2022.


\bibitem{05宮下令央01}
宮下 令央, 末石 智大, 田畑 智志, 早川 智彦, 石川 正俊: 高速ビジョンが拓くダイナミックプロジェクションマッピング技術, 電子情報通信学会 通信ソサイエティマガジン B-plus, 解説論文, No.64, pp.275-284, 2023. 


\bibitem{06田畑智志01}
田畑智志, 渡辺義浩, 石川正俊: 小型高速三次元スキャナの研究開発と将来展望, 日本ロボット工業会機関紙『ロボット』, 271号, pp.45-47, 2023.

\bibitem{ykuga41534619}
杉木章義, 空閑洋平, 竹房あつ子, 藤原一毅, 合田憲人, 中村遼, 塙敏博, 鈴村豊太郎, 宮本大輔, 田浦健次朗, 伊達進, 建部修見, データ活用社会創成に向けた基盤ソフトウェア環境の構築, 学術情報処理研究, 26, 1, pp1-9, Dec, 2022.


\end{招待論文}

\begin{受賞}{1}


\bibitem{03黄守仁01}
黄守仁,村上健一, 石川正俊: 対象の事前情報必要としない動的塗布応用に向けたロボットの実現, 第23回計測自動制御学会システムインテグレーション部門講演会(SI2022), 講演会論文集, pp.999-1001, SI2022 優秀講演賞, 2022.


\bibitem{04末石智大01}
栃岡陽麻里, 末石智大, 石川正俊: 球技スポーツの着地痕跡判定に向けた高速ビジョンを用いた落下位置予測, 第23回計測自動制御学会システムインテグレーション部門講演会(SI2022), 講演会論文集, pp.2089-2092, 優秀講演賞, 2022.


\end{受賞}

\begin{著書}{1}



\bibitem{fl-book}
Toyotaro Suzumura, Yi Zhou, Ryo Kawahara, Nathalie Baracaldo, Heiko Ludwig,
"Federated Learning for Collaborative Financial Crimes Detection",
Ludwig, H., Baracaldo, N. (eds) Federated Learning. Springer, Cham. https://doi.org/10.1007/978-3-030-96896-0\_20

\bibitem{jsai-gnn}
鈴村 豊太郎, 金刺 宏樹, 華井 雅俊, グラフニューラルネットワークの広がる活用分野, 人工知能, 2023, 38 巻, 2 号, p. 139-148, 公開日 2023/03/02, Online ISSN 2435-8614, Print ISSN 2188-2266, https://doi.org/10.11517/jjsai.38.2\_139

\end{著書}

\begin{雑誌論文}{1}

\bibitem{01石川正俊01}
Masatoshi Ishikawa, Idaku Ishii, Hiromasa Oku, Akio Namiki, Yuji Yamakawa, and Tomohiko Hayakawa: Special Issue on High-Speed Vision and its Applications, Journal of Robotics and Mechatronics, Vol.34, No.5, p.911, 2022.

\bibitem{01石川正俊02}
Taku Senoo, Atsushi Konno, Yunzhuo Wang, Masahiro Hirano, Norimasa Kishi, and Masatoshi Ishikawa: Tracking of Overlapped Vehicles with Spatio-Temporal Shared Filter for High-Speed Stereo Vision, Journal of Robotics and Mechatronics, Vol.34, No.5, pp.1033-1042, 2022.

\bibitem{01石川正俊03}
Hyuno Kim, Yuji Yamakawa, and Masatoshi Ishikawa: Seamless Multiple-Target Tracking Method Across Overlapped Multiple Camera Views Using High-Speed Image Capture, Journal of Robotics and Mechatronics, Vol.34, No.5, pp.1043-1052, 2022.

\bibitem{01石川正俊04}
Masatoshi Ishikawa: High-Speed Vision and its Applications Toward High-Speed Intelligent Systems, Journal of Robotics and Mechatronics, Vol.34, No.5, pp.912-935 , 2022.


\bibitem{02早川智彦02}
Yuriko Ezaki, Yushi Moko, Tomohiko Hayakawa, and Masatoshi Ishikawa: Angle of View Switching Method at High-Speed Using Motion Blur Compensation for Infrastructure Inspection, Journal of Robotics and Mechatronics,Vol. 34, No. 5, pp.985-996, 2022.

\bibitem{02早川智彦03}
Tomohiko Hayakawa, Yushi Moko, Kenta Morishita, Yuka Hiruma, Masatoshi Ishikawa: Tunnel Surface Monitoring System with Angle of View Compensation Function based on Self-localization by Lane Detection, Journal of Robotics and Mechatronics, Vol.34, No. 5, pp.997-1010, 2022.


\bibitem{03黄守仁02}
Kenichi Murakami, Shouren Huang, Masatoshi Ishikawa, and Yuji Yamakawa: Fully Automated Bead Art Assembly for Smart Manufacturing Using Dynamic Compensation Approach, J. Robot. Mechatron., Vol.34, No.5, pp.936-945, 2022. 

\bibitem{03黄守仁03}
Shouren Huang, Kenichi Murakami, Masatoshi Ishikawa, Yuji Yamakawa: Robotic Assistance Realizing Peg-and-Hole Alignment by Mimicking the Process of an Annular Solar Eclipse, Journal of Robotics and Mechatronics, Vol.34 No.5, pp.946-955, 2022. 


\bibitem{04末石智大02}
井上満晶, 末石智大, 松村蒼一郎, 谷内田尚司, 細井利憲, 石川正俊: 非接触マイクロサッカード検出に向けた高速追跡を用いた眼球運動検出システム, 生体医工学, Vol. 60, No. 6, pp.170-174, 2022.

\bibitem{04末石智大03}
Tomohiro Sueishi, Ryota Nishizono, and Masatoshi Ishikawa: EmnDash:A Robust High-Speed Spatial Tracking System Using a Vector-Graphics Laser Display with M-Sequence Dashed Markers, J. Robot. Mechatron., Vol.34, No.5, pp.1085-1095, 2022.


\bibitem{05宮下令央02}
Leo Miyashita, Masatoshi Ishikawa: Portable High-speed Optical Gaze Controller with Vision Chip, Journal of Robotics and Mechatronics(JRM), Vol.34, No.5, pp.1133-1140, 2022.

\bibitem{05宮下令央03}
Leo Miyashita, Yohta Kimura, Satoshi Tabata, Masatoshi Ishikawa: High-speed Depth-normal Measurement and Fusion Based on Multiband Sensing and Block Parallelization, Journal of Robotics and Mechatronics (JRM), Vol.34, No.5, pp.1111-1121, 2022.

\bibitem{05宮下令央04}
Leo Miyashita, Masatoshi Ishikawa: Real-Time Inspection of Rod Straightness and Appearance by Non-Telecentric Camera Array, Journal of Robotics and Mechatronics (JRM), Vol.34, No.5, pp.975-984, 2022.

\bibitem{05宮下令央05}
Yunpu Hu, Leo Miyashita, and Masatoshi Ishikawa: Differential Frequency Heterodyne Time-of-Flight Imaging for Instantaneous Depth and Velocity Estimation. ACM Trans. Graph. Vol.42, No.1, Article 9, pp.9, 2022.


\bibitem{06田畑智志02}
Lihui Wang, Satoshi Tabata, Hongjin Xu, Yunpu Hu, Yoshihiro Watanabe, and Masatoshi Ishikawa: Dynamic depth-of-field projection mapping method based on a variable focus lens and visual feedback, Optics Express, Vol.31, Issue 3, pp.3945-3953, 2023.

\bibitem{06田畑智志03}
Hao Xu, Satoshi Tabata, Haowen Liang, Lihui Wang, and Masatoshi Ishikawa: Accurate measurement of virtual image distance for near-eye displays based on auto-focusing, Applied Optics, Vol.61, Issue 30, pp.9093-9098, 2022.

\bibitem{06田畑智志04}
Yuping Wang, Senwei Xie, Lihui Wang, Hongjin Xu, Satoshi Tabata, and Masatoshi Ishikawa, ARSlice: Head-Mounted Display Augmented with Dynamic Tracking and Projection, Journal of Computer Science and Technology, Vol.37, Issue 3, pp.666-679, 2022.


% \bibitem{gnn-glass}
% Hayato Shiba, Masatoshi Hanai, Toyotaro Suzumura, and Takashi Shimokawabe, "BOTAN: BOnd TArgeting Network for prediction of slow glassy dynamics by machine learning relative motion." The Journal of Chemical Physics 158, no. 8, 084503, 2022.

\bibitem{osada.pccp.24.21705}
Wataru Osada, Shunsuke Tanaka, Kozo Mukai, Mitsuaki Kawamura, YoungHyun Choi, Fumihiko Ozaki, Taisuke Ozaki and Jun Yoshinobu, 
"Elucidation of the atomic-scale processes of dissociative adsorption and spillover of hydrogen on the single atom alloy catalyst Pd/Cu(111)",
Physical Chemistry and Chemical Physics 24, 36, 21705-21713, 2022.

\bibitem{hirai.jacs.144.17857}
Daigorou Hirai, Keita Kojima, Naoyuki Katayama, Mitsuaki Kawamura, Daisuke Nishio-Hamane, and Zenji Hiroi,
"Linear Trimer Molecule Formation by Three-Center-Four-Electron Bonding in a Crystalline Solid RuP",
Journal of the American Chemical Society 144, 39, 17857-17864, 2022.

\bibitem{koshoji.prm.6.114802}
Ryotaro Koshoji, Masahiro Fukuda, Mitsuaki Kawamura, Taisuke Ozaki,
"Prediction of quaternary hydrides based on densest ternary sphere packings",
Physical Review Materials 6, 11, 114802.1-9, 2022.

\bibitem{kobayashi1-1}
Wenjing Li, Haoran Zhang, Ryosuke Shibasaki,  Jinyu Chen and Hill Hiroki Kobayashi,  "Mining individual significant places from historical trajectory data", Handbook of Mobility Data Mining, Jan, 2023.

\bibitem{kobayashi1-2}
Wenjing Li, Haoran Zhang, Ryosuke Shibasaki,  Jinyu Chen and Hill Hiroki Kobayashi,  "Mobility pattern clustering with big human mobility data", Handbook of Mobility Data Mining, Jan, 2023.

\bibitem{kobayashi1-3}
Wenjing Li, Haoran Zhang, Jinyu Chen, Peiran Li, Yuhao Yao, Xiaodan Shi,  Mariko Shibasaki, Hill Hiroki Kobayashi, Xuan Song and Ryosuke Shibasaki,  "Metagraph-Based Life Pattern Clustering With Big Human Mobility Data", IEEE Transactions on Big Data, Feb, 2023.

\bibitem{JIANG1-1}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Xuan Song, and Ryosuke Shibasaki, "Predicting Citywide Crowd Dynamics at Big Events: A Deep Learning System", ACM Trans. Intell. Syst. Technol. (TIST), 13, 2, Article 21, April 2022.
\bibitem{JIANG1-2}
Zipei Fan, Chuang Yang, Zhiwen Zhang, Xuan Song, Yinghao Liu, Renhe Jiang, Quanjun Chen, and Ryosuke Shibasaki, "Human Mobility-based Individual-level Epidemic Simulation Platform", ACM Trans. Spatial Algorithms Syst. (TSAS), 8, 3, Article 19, September 2022.
\bibitem{JIANG1-3}
Chuang Yang, Zhiwen Zhang, Zipei Fan, Renhe Jiang, Quanjun Chen, Xuan Song, Ryosuke Shibasaki, "EpiMob: Interactive Visual Analytics of Citywide Human Mobility Restrictions for Epidemic Control", IEEE Transactions on Visualization and Computer Graphics (TVCG), 2022.
\bibitem{JIANG1-4}
Yudong Tao, Chuang Yang, Tianyi Wang, Erik Coltey, Yanxiu Jin, Yinghao Liu, Renhe Jiang, Zipei Fan, Xuan Song, Ryosuke Shibasaki, Shu-Ching Chen, Mei-Ling Shyu, Steven Luis, "A Survey on Data-Driven COVID-19 and Future Pandemic Management", ACM Computing Surveys (CSUR), 2022.
\bibitem{JIANG1-5}
Yongkang Li, Zipei Fan, Du Yin, Renhe Jiang, Jinliang Deng, Xuan Song, "HMGCL: Heterogeneous Multigraph Contrastive Learning for LBSN Friend Recommendation", World Wide Web (WWW), 2022.
\bibitem{JIANG1-6}
Renhe Jiang, Quanjun Chen, Zekun Cai, Zipei Fan, Xuan Song, Kota Tsubouchi, and Ryosuke Shibasaki, “Will You Go Where You Search? A Deep Learning Framework for Estimating User Search-and-Go Behavior”, Neurocomputing, Volume 472, 2022, Pages 338-348.
\bibitem{JIANG1-7}
Jinliang Deng, Xiusi Chen, Renhe Jiang, Xuan Song, Ivor W. Tsang, "A Multi-view Multi-task Learning Framework for Multi-variate Time Series Forecasting", IEEE Transactions on Knowledge and Data Engineering (TKDE), 2022.


\bibitem{feta}
Bastos, Anson, Abhishek Nadgeri, Kuldeep Singh, Hiroki Kanezashi, Toyotaro Suzumura, and Isaiah Onando Mulang, "How Expressive Are Transformers in Spectral Domain for Graphs?", Transactions on Machine Learning Research (TMLR) ISSN 2835-8856, Journal of Machine Learning Research, 2022.

\bibitem{Uesaka2023HCII}
Uesaka L, Khatiwada AP, Shimotoku D, Parajuli LK, Pandey MR, Kobayashi HH (2023). Applications of Bioacoustics Human Interface System for Wildlife Conservation in Nepal. Accepted for publication in Human Computer Interaction (HCI) International 2023.


\bibitem{li2022neural}
Irene Li, Jessica Pan, Jeremy Goldwasser, Neha Verma, Wai Pan Wong, Muhammed Yavuz Nuzumlalı, Benjamin Rosand, Yixin Li, Matthew Zhang, David Chang, R. Andrew Taylor, Harlan M. Krumholz, Dragomir Radev, "Neural Natural Language Processing for unstructured data in electronic health records: A review", Computer Science Review, volume 46, 2022.

\end{雑誌論文}

\begin{査読付}{1}


\bibitem{02早川智彦04}
Kairi Mine, Chika Nishimura, Tomohiko Hayakawa, Satoshi Yawata, Dai Watanabe, and Masatoshi Ishikawa: Migration correction technique using spatial information of neuronal images in fiber-inserted mouse under free-running behavior, Conf. on Neural Imaging and Sensing 2023, SPIE Photonics West BiOS／Proc. SPIE, Vol.1236522, pp.1236522: 1-1236522: 5, 2023.

\bibitem{02早川智彦05}
Yushan Ke, Yushi Moko, Yuka Hiruma, Tomohiko Hayakawa, Masatoshi Ishikawa: Silk-printed retroreflective markers for infrastructure-maintenance vehicles in tunnels, SPIE Smart Structures and Materials + Nondestructive Evaluation 2022 On Demand (Online), Paper 12046-18, 2022.

\bibitem{02早川智彦06}
Yushan Ke, Yushi Moko, Yuka Hiruma, Tomohiko Hayakawa, Elgueta Scarlet, Masatoshi Ishikawa: Silk-printed retroreflective markers for infrastructure-maintenance vehicles in curved tunnels, SPIE Smart Structures and Materials + Nondestructive Evaluation 2023, Paper 12483-40, 2023.


\bibitem{05宮下令央06}
宮下 令央, 田畑 智志, 石川 正俊: パラレルバスパターンによる高速低遅延3次元形状計測, 計測自動制御学会, 第39回 センシングフォーラム, 1B1-1, 予稿集 pp.49-54, 2022.

\bibitem{05宮下令央07}
Leo Miyashita, Satoshi Tabata, Masatoshi Ishikawa: High-speed and Low-latency 3D Sensing with a Parallel-bus Pattern, International Conference on 3D Vision(3DV2022), 2022.

\bibitem{05宮下令央08}
Leo Miyashita, Kentaro Fukamizu, Yuki Kubota, Tomohiko Hayakawa, Masatoshi Ishikawa: Real-time animation display based on optical illusion by overlaid luminance changes, SPIE Optical Architectures for Displays and Sensing in Augmented, Virtual, and Mixed Reality(AR, VR, MR)IV, Oral, paper 12449-8, 2023.


\bibitem{06田畑智志05}
Yuping Wang, Senwei Xie, Lihui Wang, Hongjin Xu, Satoshi Tabata, Masatoshi Ishikawa: Head-Mounted Display Augmented with Dynamic Tracking and Projection, The 10th international conference on Computational Visual Media(CVM 2022), 2022.


% \bibitem{xsig-limin-hanai}
% Limin Wang, Masatoshi Hanai, Toyotaro Suzumura, Shun Takashige, Kenjiro Taura, "On Data Imbalance in Molecular Property Prediction with Pre-training" xSIG 2023 (submitted)

% \bibitem{xsig-takashige-hanai}
% Shun Takashige, Masatoshi Hanai, Toyotaro Suzumura, Limin Wang, Kenjiro Taura, "Is Self-Supervised Pretraining Good for Extrapolation in Molecular Property Prediction?" xSIG 2023 (submitted)

% \bibitem{stgtrans-xiaohang}
% Xiaohang Xu, Toyotaro Suzumura, Jiawei Yong, Masatoshi Hanai, Chuang Yang, Hiroki Kanezashi, Renhe Jiang, Shintaro Fukushima, "Spatial-Temporal Graph Transformer for Next Point-of-Interest Recommendation", Machine Learning and Knowledge Discovery in Databases: European Conference, (ECML-PKDD), 2023 (submitted)

\bibitem{kobayashi2-1}
Daisuk\'e Shimotoku, Tian Yuan, Laxmi Kumar Parajuli and Hill Hiroki Kobayashi, "Participatory Sensing Platform Concept for Wildlife Animals in the Himalaya Region, Nepal", Proceedings of 2022 International Conference on Human-Computer Interaction (HCII 2022), 2022.  

\bibitem{kobayashi2-2}
Qaiser Anwar, Muhammad Hanif, Daisuk\'e Shimotoku and  Hiroki Kobayashi, "Driver awareness collision/proximity detection system for heavy vehicles based on deep neural network", International Symposium on Intelligent Unmanned Systems and Artificial Intelligence (SIUSAI 2022) , 2022.  

\bibitem{kobayashi2-3}
Usman Haider, Muhammad Hanif, Laxmi Kumar Parajuli, Hill Hiroki Kobayashi, Daisuk\'e Shimotoku, Ahmar Rashid and Sonia Safeer, "Bioacoustics signal classification using hybrid feature space with machine learning",  International Conference on Computer and Automation Engineering (ICCAE 2023), 2023.  

\bibitem{ykuga40356877}
空閑洋平, 中村遼, 遠隔会議システムの計測データを用いた広域ネットワーク品質計測, インターネットと運用技術シンポジウム論文集, 2022, Dec, 2022.

\bibitem{ykuga39987672}
Shu Anzai, Masanori Misono, Ryo Nakamura, Yohei Kuga, Takahiro Shinagawa, Towards isolated execution at the machine level, Proceedings of the 13th ACM SIGOPS Asia-Pacific Workshop on Systems, 23 Aug, 2022.

\bibitem{ykuga36919054}
Yukito Ueno, Ryo Nakamura, Yohei Kuga, Hiroshi Esaki, Pktpit: separating routing and packet transfer for fast and scalable software routers, Proceedings of the 37th ACM/SIGAPP Symposium on Applied Computing, 25 Apr, 2022.

\bibitem{JIANG2-1}
Renhe Jiang, Zhaonan Wang, Jiawei Yong, Puneet Jeph, Quanjun Chen, Yasumasa Kobayashi,
Xuan Song, Shintaro Fukushima, Toyotaro Suzumura, "Spatio-Temporal Meta-Graph Learning for Traffic Forecasting", Proceedings of Thirty-Seventh AAAI Conference on Artificial Intelligence (AAAI), 2023.
\bibitem{JIANG2-2}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki, "Yahoo! Bousai Crowd Data: A Large-Scale Crowd Density and Flow Dataset in Tokyo and Osaka", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-3}
Xinchen Hao, Renhe Jiang, Jiewen Deng, Xuan Song, "The Impact of COVID-19 on Human Mobility: A Case Study on New York", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-4}
Zheng Dong, Quanjun Chen, Renhe Jiang, Hongjun Wang, Xuan Song, Hao Tian, "Learning Latent Road Correlations from Trajectories", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-5}
Zipei Fan, Xiaojie Yang, Wei Yuan, Renhe Jiang, Quanjun Chen, Xuan Song, Ryosuke Shibasaki, "Online Trajectory Prediction for Metropolitan Scale Mobility Digital Twin", Proc. of 30th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems (SIGSPATIAL), 2022. 
\bibitem{JIANG2-6}
Haoyuan Ma, Mintao Zhou, Xiaodong Ouyang, Du Yin, Renhe Jiang, Xuan Song, "Forecasting Regional Multimodal Transportation Demand with Graph Neural Networks: An Open Dataset", Proc. of 2022 IEEE International Intelligent Transportation Systems Conference (ITSC), 2022.
\bibitem{JIANG2-7}
Qi Cao, Renhe Jiang, Chuang Yang, Zipei Fan, Xuan Song, Ryosuke Shibasaki, "MepoGNN: Metapopulation Epidemic Forecasting with Graph Neural Networks", Proceedings of the European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML PKDD), 2022. 
\bibitem{JIANG2-8}
Hangli Ge, Lifeng Lin, Renhe Jiang, Takashi Michikata, Noboru Koshizuka, "Multi-weighted Graphs Learning for Passenger Count Prediction on Railway Network," 2022 IEEE 46th Annual Computers, Software, and Applications Conference (COMPSAC), 2022.


\bibitem{sigir}
Md Mostafizur Rahman, Daisuke Kikuta, Satyen Abrol, Yu Hirate, Toyotaro Suzumura, Pablo Loyola, Takuma Ebisu and Manoj Kondapaka, "Exploring 360-Degree View of Customers for Lookalike Modeling",  SIGIR'23 (The 46th International ACM
SIGIR Conference on Research and Development in Information
Retrieval) 


\bibitem{aaai-deft}
Anson Bastos, Abhishek Nadgeri, Kuldeep Singh, Toyotaro Suzumura, Manish Singh,
"Learnable Spectral Wavelets on Dynamic Graphs to Capture Global Interactions"
The 37th AAAI Conference on Artificial Intelligence (AAAI), 2023.

\bibitem{aaai-megacrn}
Renhe Jiang, Zhaonan Wang, Jiawei Yong, Puneet Jeph, Quanjun Chen, Yasumasa Kobayashi, Xuan Song, Shintaro Fukushima, Toyotaro Suzumura,
"Spatio-Temporal Meta-Graph Learning for Traffic Forecasting"
37th AAAI Conference on Artificial Intelligence (AAAI), 2023.

\bibitem{kg-kp}
Anson Bastos, Kuldeep Singh, Abhishek Nadgeri, Johannes Hoffart, Toyotaro Suzumura, Manish Singh,
"Can Persistent Homology provide an efficient alternative for Evaluation of Knowledge Graph Completion Methods?"
In proceedings of The Web Conference (WWW), 2023.


\bibitem{gqsm}
Chinthaka Weerakkody, Miyuru Dayarathna, Sanath Jayasena, Toyotaro Suzumura
"Guaranteeing Service Level Agreements for Triangle Counting via Observation-based Admission Control Algorithm", IEEE 15th International Conference on Cloud Computing (CLOUD 2022), 2022.

\bibitem{mdx}
Toyotaro Suzumura, Akiyoshi Sugiki, Hiroyuki Takizawa, Akira Imakura, Hiroshi Nakamura, Kenjiro Taura, Tomohiro Kudoh, Toshihiro Hanawa, Yuji Sekiya, Hiroki Kobayashi, Shin Matsushima, Yohei Kuga, Ryo Nakamura, Renhe Jiang, Junya Kawase, Masatoshi Hanai, Hiroshi Miyazaki, Tsutomu Ishizaki, Daisuke Shimotoku, Daisuke Miyamoto, Kento Aida, Atsuko Takefusa, Takashi Kurimoto, Koji Sasayama, Naoya Kitagawa, Ikki Fujiwara, Yusuke Tanimura, Takayuki Aoki, Toshio Endo, Satoshi Ohshima, Keiichiro Fukazawa, Susumu Date, Toshihiro Uchibayashi,
"mdx: A Cloud Platform for Supporting Data Science and Cross-Disciplinary Research Collaborations", 2022 IEEE Intl Conf on Cloud and Big Data Computing, (CBDCom), 2022.

\bibitem{botan}
Hayato Shiba, Masatoshi Hanai, Toyotaro Suzumura, and Takashi Shimokawabe, "BOTAN: BOnd TArgeting Network for prediction of slow glassy dynamics by machine learning relative motion." The Journal of Chemical Physics 158, no. 8, 084503, 2022.

\bibitem{eth-gnn}
Hiroki Kanezashi, Toyotaro Suzumura, Xin Liu, Takahiro Hirofuchi,
"Ethereum Fraud Detection with Heterogeneous Graph Neural Networks"
28TH ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD'22), Workshop on Mining and Learning with Graphs, 2022.

\bibitem{stgtrans}
Xiaohang Xu, Toyotaro Suzumura, Jiawei Yong, Masatoshi Hanai, Chuang Yang, Hiroki Kanezashi, Renhe Jiang, Shintaro Fukushima, "Spatial-Temporal Graph Transformer for Next Point-of-Interest Recommendation", Machine Learning and Knowledge Discovery in Databases: European Conference, (ECML-PKDD), 2023 (submitted)


\bibitem{xsig-limin}
Limin Wang, Masatoshi Hanai, Toyotaro Suzumura, Shun Takashige, Kenjiro Taura, "On Data Imbalance in Molecular Property Prediction with Pre-training" xSIG 2023 (cross-disciplinary workshop on computing Systems, Infrastructures, and programminG)  (submitted)

\bibitem{xsig-takashige}
Shun Takashige, Masatoshi Hanai, Toyotaro Suzumura, Limin Wang, Kenjiro Taura, "Is Self-Supervised Pretraining Good for Extrapolation in Molecular Property Prediction?" xSIG 2023 (cross-disciplinary workshop on computing Systems, Infrastructures, and programminG) (submitted)


% \bibitem{suzumura-sc2021}
% Venkatesan T. Chakaravarthy, Shivmaran S. Pandian, Saurabh Raje, Yogish Sabharwal, Toyotaro Suzumura, Shashanka Ubaru, 
% "Efficient scaling of dynamic graph neural networks". SC2021(The International Conference for High Performance Computing, Networking, Storage, and Analysis)

% \bibitem{suzumura-smds21}
% Shilei Zhang, Toyotaro Suzumura, Li Zhang, "DynGraphTrans: Dynamic Graph Embedding via Modified Universal Transformer Networks for Financial Transaction Data", IEEE SMDS 2021 (International Conference on Smart Data Services) 

\bibitem{feng2022diffuser}
Aosong Feng and Irene Li and Yuang Jiang andRex  Ying, "Diffuser: Efficient Transformers with Multi-hop Attention Diffusion for Long Sequences", Proceedings of Thirty-Seventh AAAI Conference on Artificial Intelligence (AAAI), 2023.

\end{査読付}


\begin{発表}{1}


\bibitem{01石川正俊05}
Taku Senoo, Atsushi Konno, Yunzhuo Wang, Masahiro Hirano, Norimasa Kishi, and Masatoshi Ishikawa: Automotive Tracking with High-speed Stereo Vision Based on a Spatiotemporal Shared Filter, the 2022 26th International Conference on System Theory, Control and Computing (ICSTCC2022), Proceedings, pp.613-618, 2022.


\bibitem{02早川智彦07}
蛭間友香, 早川智彦, 石川正俊: 映像遅延および空間情報を制御可能な手の高速撮像・投影システムの構築, 第27回日本バーチャルリアリティ学会大会(vrsj2022)(札幌, 2022.9.14)／予稿集, 3F5-4, 2022.


\bibitem{03黄守仁04}
黄守仁, 村上健一, 石川正俊: 対象の事前情報必要としない動的塗布応用に向けたロボットの実現, 第23回計測自動制御学会システムインテグレーション部門講演会(SI2022), 講演会論文集, pp.999-1001, 2022.

\bibitem{03黄守仁05}
村上健一,黄守仁,石川正俊,山川雄司: 動的補償を用いたビーズピッキング, 第40回日本ロボット学会学術講演会 (RSJ2022), 予稿集, 4C1-05, 2022.

\bibitem{03黄守仁06}
Shouren Huang, Yongpeng Cao, Kenichi Murakami, Masatoshi Ishikawa,Yuji Yamakawa: Bimanual Coordination Protocol for the Inter-Limb Transmission of Force Feedback, 第40回日本ロボット学会学術講演会 (RSJ2022), 予稿集, 2C1-05, 2022.


\bibitem{04末石智大04}
末石智大, 井上満晶, 谷内田尚司, 石川正俊: 照明制御に基づく動的眼球高速トラッキングによる明瞳孔微振動画像計測, 動的画像処理実利用化ワークショップ2023(DIA2023), 講演論文集, pp.133-136, IS1-20, 2023.

\bibitem{04末石智大05}
栃岡陽麻里, 末石智大, 石川正俊: 球技スポーツの着地痕跡判定に向けた高速ビジョンを用いた落下位置予測, 第23回計測自動制御学会システムインテグレーション部門講演会(SI2022), 講演会論文集, pp.2089-2092, 2022.

\bibitem{04末石智大06}
末石智大, 石川正俊: 縞状同心円パターンを用いた可変焦点制御系のカメラ校正手法, 第23回計測自動制御学会システムインテグレーション部門講演会(SI2022), 講演会論文集, pp.2093-2097, 2022.

\bibitem{04末石智大07}
井上満晶, 末石智大, 松村蒼一郎, 谷内田尚司, 細井利憲, 石川正俊: 非接触マイクロサッカード検出に向けた高速追跡を用いた眼球運動検出システム, 生体医工学シンポジウム2022(オンライン), 予稿・抄録集, p.13, 1A-11, 2022.

\bibitem{04末石智大08}
末石智大, 石川正俊: 高速光学系制御と対称的ドットマーカによる卓球回転実時間計測, 第40回日本ロボット学会学術講演会 (RSJ2022), 予稿集, 2B1-08, 2022.


\bibitem{06田畑智志0６}
田畑智志, 渡辺義浩, 石川正俊: 小型高速三次元スキャナの開発, 第40回日本ロボット学会学術講演会(RSJ2022), 予稿集, 2B1-07, 2022.


\bibitem{ykuga41835081}
中村遼, 空閑洋平, 複数コネクションを用いる高速なscpの実装, 研究報告システムソフトウェアとオペレーティング・システム（OS）, Feb, 2023.

\bibitem{ykuga41835070}
空閑洋平, 中村遼, ソフトウェアメモリを用いたNVMeコマンドのキャプチャ, 研究報告システムソフトウェアとオペレーティング・システム（OS）, Feb, 2023.


\bibitem{sms}
脇 聡志, 鈴村 豊太郎, 金刺 宏樹, 小林 秀, "強化学習によるマッチング数を最大化するジョブ推薦システム." 第37回人工知能学会全国大会 (2023),  一般社団法人 人工知能学会, (2023年6月発表予定)


\bibitem{li2023nnkgc}
Zihui Li and Boming Yang and Toyotaro Suzumura, "NNKGC: Improving Knowledge Graph Completion with Node Neighborhoods", arXiv preprint, 2023.

\end{発表}


\begin{報道}{1}


\bibitem{06田畑智志07}
田畑智志: 毎秒1000回撮像で立体計測 小型高速3Dスキャナー ロボアームの高速操作向け 東大など開発, 日刊工業新聞, 2022年9月27日.


\end{報道}
