\begin{雑誌論文}{1}
\bibitem{JIANG1-1}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Xuan Song, and Ryosuke Shibasaki, "Predicting Citywide Crowd Dynamics at Big Events: A Deep Learning System", ACM Trans. Intell. Syst. Technol. (TIST), 13, 2, Article 21, April 2022.
\bibitem{JIANG1-2}
Zipei Fan, Chuang Yang, Zhiwen Zhang, Xuan Song, Yinghao Liu, Renhe Jiang, Quanjun Chen, and Ryosuke Shibasaki, "Human Mobility-based Individual-level Epidemic Simulation Platform", ACM Trans. Spatial Algorithms Syst. (TSAS), 8, 3, Article 19, September 2022.
\bibitem{JIANG1-3}
Chuang Yang, Zhiwen Zhang, Zipei Fan, Renhe Jiang, Quanjun Chen, Xuan Song, Ryosuke Shibasaki, "EpiMob: Interactive Visual Analytics of Citywide Human Mobility Restrictions for Epidemic Control", IEEE Transactions on Visualization and Computer Graphics (TVCG), 2022.
\bibitem{JIANG1-4}
Yudong Tao, Chuang Yang, Tianyi Wang, Erik Coltey, Yanxiu Jin, Yinghao Liu, Renhe Jiang, Zipei Fan, Xuan Song, Ryosuke Shibasaki, Shu-Ching Chen, Mei-Ling Shyu, Steven Luis, "A Survey on Data-Driven COVID-19 and Future Pandemic Management", ACM Computing Surveys (CSUR), 2022.
\bibitem{JIANG1-5}
Yongkang Li, Zipei Fan, Du Yin, Renhe Jiang, Jinliang Deng, Xuan Song, "HMGCL: Heterogeneous Multigraph Contrastive Learning for LBSN Friend Recommendation", World Wide Web (WWW), 2022.
\bibitem{JIANG1-6}
Renhe Jiang, Quanjun Chen, Zekun Cai, Zipei Fan, Xuan Song, Kota Tsubouchi, and Ryosuke Shibasaki, “Will You Go Where You Search? A Deep Learning Framework for Estimating User Search-and-Go Behavior”, Neurocomputing, Volume 472, 2022, Pages 338-348.
\bibitem{JIANG1-7}
Jinliang Deng, Xiusi Chen, Renhe Jiang, Xuan Song, Ivor W. Tsang, "A Multi-view Multi-task Learning Framework for Multi-variate Time Series Forecasting", IEEE Transactions on Knowledge and Data Engineering (TKDE), 2022.

\end{雑誌論文}

\begin{査読付}{1}
\bibitem{JIANG2-1}
Renhe Jiang, Zhaonan Wang, Jiawei Yong, Puneet Jeph, Quanjun Chen, Yasumasa Kobayashi,
Xuan Song, Shintaro Fukushima, Toyotaro Suzumura, "Spatio-Temporal Meta-Graph Learning for Traffic Forecasting", Proceedings of Thirty-Seventh AAAI Conference on Artificial Intelligence (AAAI), 2023.
\bibitem{JIANG2-2}
Renhe Jiang, Zekun Cai, Zhaonan Wang, Chuang Yang, Zipei Fan, Quanjun Chen, Kota Tsubouchi, Xuan Song, Ryosuke Shibasaki, "Yahoo! Bousai Crowd Data: A Large-Scale Crowd Density and Flow Dataset in Tokyo and Osaka", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-3}
Xinchen Hao, Renhe Jiang, Jiewen Deng, Xuan Song, "The Impact of COVID-19 on Human Mobility: A Case Study on New York", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-4}
Zheng Dong, Quanjun Chen, Renhe Jiang, Hongjun Wang, Xuan Song, Hao Tian, "Learning Latent Road Correlations from Trajectories", Proc. of 2022 IEEE International Conference on Big Data (BigData), 2022.
\bibitem{JIANG2-5}
Zipei Fan, Xiaojie Yang, Wei Yuan, Renhe Jiang, Quanjun Chen, Xuan Song, Ryosuke Shibasaki, "Online Trajectory Prediction for Metropolitan Scale Mobility Digital Twin", Proc. of 30th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems (SIGSPATIAL), 2022. 
\bibitem{JIANG2-6}
Haoyuan Ma, Mintao Zhou, Xiaodong Ouyang, Du Yin, Renhe Jiang, Xuan Song, "Forecasting Regional Multimodal Transportation Demand with Graph Neural Networks: An Open Dataset", Proc. of 2022 IEEE International Intelligent Transportation Systems Conference (ITSC), 2022.
\bibitem{JIANG2-7}
Qi Cao, Renhe Jiang, Chuang Yang, Zipei Fan, Xuan Song, Ryosuke Shibasaki, "MepoGNN: Metapopulation Epidemic Forecasting with Graph Neural Networks", Proceedings of the European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML PKDD), 2022. 
\bibitem{JIANG2-8}
Hangli Ge, Lifeng Lin, Renhe Jiang, Takashi Michikata, Noboru Koshizuka, "Multi-weighted Graphs Learning for Passenger Count Prediction on Railway Network," 2022 IEEE 46th Annual Computers, Software, and Applications Conference (COMPSAC), 2022.
\end{査読付}

